jaod
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Build Status](https://travis-ci.org/ropenscilabs/jaod.svg?branch=master)](https://travis-ci.org/ropenscilabs/jaod)

`jaod` - R client for [Directory of Open Access Journals API](https://doaj.org/api/v1/docs)

## installation

stable CRAN version

```{r eval=FALSE}
install.packages("jaod")
```

development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/jaod")
```

```{r}
library("jaod")
```

## search journals

```{r}
jaod_journal_search(query = "bibjson.keywords:heritage")
```

## get journal by id

```{r}
out <- jaod_journal(id = "f3f2e7f23d444370ae5f5199f85bc100")
names(out$bibjson)
```

```{r}
out$bibjson$archiving_policy
out$bibjson$apc
out$bibjson$article_statistics
out$bibjson$author_publishing_rights
```


## search articles

```{r}
jaod_article_search(query = "license:CC-BY")
```

## get article by id

```{r}
out <- jaod_article(id = "0004c9e6a3c64ec9848607e51b7edbca")
names(out$bibjson)
```

```{r}
out$bibjson$author
out$bibjson$link
out$bibjson$identifier
out$bibjson$subject
```


## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/jaod/issues).
* License: MIT
* Get citation information for `jaod` in R doing `citation(package = jaod')`
* Please note that this project is CONDUCT.md). By participating in this project you agree to abide by its terms.
