---
title: "Directory of Open Access Journals"
author: "Lluís Revilla Sancho"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Directory of Open Access Journals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

# Installation

You can install the stable CRAN version

```{r eval=FALSE}
install.packages("jaod")
```

Or the development version:

```{r eval=FALSE}
devtools::install_github("ropensci/jaod")
```

```{r}
library("jaod")
```

# Searching journals

To search for a journal you can use the `jaod_journal_search`,
which provides information abut the search result, query and relevant information.
For instance looking for heritage:

```{r}
bibliography <- jaod_journal_search(query = "bibjson.keywords:heritage")
bibliography$results
```

We can see with `bibliography$total` the total amount of results with `bibliography$total`.
On the `bibliography$results` we have the information about each entry, title, creation, update, title, subject.
We have for instance the id of the journal in `bibliography$results$id`

## Getting detailed information about a journal.

Once we have a journal we might be interested in more information.
We can retrieve who administrate it, when was last updated, other bibliographic references:

```{r}
journal <- jaod_journal(id = bibliography$result$id[1])
```

So for intance looking at the subject `journal$bibjson$subject` we can see that
is based on Ethnology, social and cultural antrophology.
Or that author doesn't keep the publishing rights (`journal$bibjson$author_publishing_rights$publishing_rights`)

# Searching articles

We might be looking for an article with some licensing

```{r}
articles <- jaod_article_search(query = "license:CC-BY", sort = "bibjson.year:desc")
articles$results
```

So we learn that there are

```{r}
articles$total
```

with CC-BY license.

Or to know the dois, or other identifiers:

```{r}
articles$results$bibjson.identifier[[1]]
```

## Searching more detailed information about an article

If you are interested in information about the article you can use the id:

```{r}
article <- jaod_article(articles$results$id[1])
```

We can access the title, authors, and more.


# SessionInfo {-}

```{r}
sessionInfo()
```
